Comparison of Catalogs

### 2024-12-16 compare/compare.qmd
presentations
one for Chatzidimitriou, one for akras team

---
title: "Comparison of Catalogs"
format: 
  html: 
    code-fold: true
    html-math-method: katex
  pdf: default
  arxiv-pdf:
    keep-tex: true    
toc: true
toc-depth: 3
theme: minti
bibliography: ../My_Library.bib
execute: 
  echo: false
  eval: true
  warning: false
---

>>>>

---
title: "Comparison of Catalogs"
format: 
  html: 
    code-fold: true
    html-math-method: katex
  pdf: default
  arxiv-pdf:
    keep-tex: true    
toc: true
toc-depth: 3
theme: minti
bibliography: ../My_Library.bib
execute: 
  echo: false
  eval: true
  warning: false
---
```{python}

### 2024-12-16 compare/compare.tex
presentations
one for Chatzidimitriou, one for akras team

The dataset we are going to use for the comparison (inner join) consists
of 288 galaxies and 168 columns with their physical characteristics.

@@

\begin{longtable}[]{@{}lr@{}}
\toprule\noalign{}
Table & Number of galaxies \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Inner join & 288 \\
Outer join & 2901 \\
LVG & 1316 \\
HECATE & 2901 \\
Unique galaxies in LVG & 1028 \\
Unique Galaxies in Hecate & 2613 \\
\end{longtable}

@@

Completeness (HECATE)= 10 \%

Completeness (LVG)= 22 \%

@@

Combined Completeness
=\(\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LVG}}\)=
80 \%

@@

\begin{longtable}[]{@{}llll@{}}
\toprule\noalign{}
& inc & INCL & Percentage Change {[}\%{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 287 & 209 & 202 \\
mean & 60 & 59 & -0 \\
std & 19 & 23 & 0 \\
min & 9 & 0 & -3 \\
50\% & 60 & 59 & 0 \\
max & 90 & 90 & 1 \\
\end{longtable}

>>>>

The dataset we are going to use for the comparison (inner join) consists
of 3934 galaxies and 172 columns with their physical characteristics.

@@

\begin{longtable}[]{@{}lr@{}}
\toprule\noalign{}
Table & Number of galaxies \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Inner join & 3934 \\
Outer join & 3934 \\
LVG & 1321 \\
HECATE & 2901 \\
Unique galaxies in LVG & 1033 \\
Unique Galaxies in Hecate & 2613 \\
\end{longtable}

@@

Completeness (HECATE)= 136 \%

Completeness (LVG)= 298 \%

@@

Combined Completeness
=\(\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LVG}}\)=
108 \%

@@

\begin{longtable}[]{@{}llll@{}}
\toprule\noalign{}
& inc & INCL & Percentage Change {[}\%{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 1308 & 1994 & 202 \\
mean & 55 & 51 & -0 \\
std & 20 & 20 & 0 \\
min & 0 & 0 & -3 \\
50\% & 54 & 50 & 0 \\
max & 90 & 90 & 1 \\
\end{longtable}
